---
title: "bubbles"
output: html_document
date: "2024-03-17"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
```


```{r}
education <- read.csv("/Users/andyouyang/Documents/bubbles final.csv")

education$Agree.Neutral.Disagree <- factor(education$Agree.Neutral.Disagree, levels = c("agree", "neutral", "disagree"))
unique_rows <- education[!duplicated(education$Reddit.ink.to.post), ]
```


# sentiment vs views
```{r}

# aggregrates the total, useless

# ggplot(unique_rows, aes(x = Agree.Neutral.Disagree, y = Total.Views, fill = Agree.Neutral.Disagree)) +
#   geom_bar(stat = "identity") +
#   labs(x = "Agree/Neutral/Disagree", y = "Total Views") +
#   theme_minimal()

ggplot(unique_rows, aes(x = as.numeric(Agree.Neutral.Disagree), y = Total.Views, color = Agree.Neutral.Disagree)) +
  geom_jitter(aes(color = as.factor(Agree.Neutral.Disagree)), width = 0.2, height = 0, alpha = 0.9) +
  geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = FALSE, color = "black") +  # polynomial regr line, degree 2
  labs(x = "Agree/Neutral/Disagree", y = "Total Views", title = "Total Views vs Sentiment of Post Towards Topic of CMU") +
  scale_x_continuous(breaks = 1:3, labels = levels(unique_rows$Agree.Neutral.Disagree)) +  # x-axis breaks and labels 
  scale_color_manual(values = c("red", "green", "blue")) +
  theme_minimal() 


ggplot(unique_rows, aes(x = as.numeric(Agree.Neutral.Disagree), y = Total.Views, color = as.factor(subreddit))) +
  geom_jitter(aes(color = as.factor(subreddit)), width = 0.2, height = 0, alpha = 0.9) +
  geom_smooth(data = subset(unique_rows, subreddit == "CMU"), method = "lm", formula = y ~ poly(x, 2), se = FALSE, color = "aquamarine3") +
  geom_smooth(data = subset(unique_rows, subreddit == "ApplyingToCollege"), method = "lm", formula = y ~ poly(x, 2), se = FALSE, color = "coral3") +
  labs(x = "Agree/Neutral/Disagree", y = "Total Views", title = "Total Views vs Sentiment of Post Towards Topic of CMU by 
       Subreddit") +
  scale_x_continuous(breaks = 1:3, labels = levels(unique_rows$Agree.Neutral.Disagree)) +  # Specify x-axis breaks and labels 
  scale_color_manual(name = "Subreddit",
                     values = c("CMU" = "aquamarine3", "ApplyingToCollege" = "coral3")) +  # Changing legend names
  theme_minimal()

# shows each one as bar
ggplot(unique_rows, aes(x = Reddit.ink.to.post, y = Total.Views, fill = Agree.Neutral.Disagree)) +
  geom_bar(stat = "identity") +
  facet_wrap(~ Agree.Neutral.Disagree, scales = "free_x") +
  labs(x = "", y = "Total Views") +
  facet_wrap(~ subreddit, scales = "free_x") +
  theme_minimal() +
  theme(axis.text.x = element_blank(),    # Remove x-axis text
        axis.title.x = element_blank())   # Remove x-axis title

```

```{r}

ggplot(unique_rows, aes(x = as.factor(Agree.Neutral.Disagree), y = Total.Views, color = as.factor(Agree.Neutral.Disagree))) +
  geom_boxplot(color = "gray") +  # Setting the color of the boxplot
  geom_jitter(aes(color = as.factor(Agree.Neutral.Disagree)), width = 0.2, height = 0, alpha = 0.9) +
  scale_color_manual(values = c("green", "red", "blue")) +  # Setting the colors for each boxplot
  labs(x = "Agree/Neutral/Disagree", y = "Total Views") +
  scale_x_discrete(labels = c("Agree", "Neutral", "Disagree")) +  
  geom_smooth(method = "lm", formula = y ~ poly(as.numeric(x), 2), se = FALSE, aes(color = "black")) +  
  theme_minimal()

# cant add regression here
```


# sentiment vs upvote count
``` {r}
ggplot(unique_rows, aes(x = as.numeric(Agree.Neutral.Disagree), y = Upvote.count, color = Agree.Neutral.Disagree)) +
  geom_jitter(aes(color = as.factor(Agree.Neutral.Disagree)), width = 0.2, height = 0, alpha = 0.9) +
  geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = FALSE, color = "black") +  # Add a polynomial regression line of degree 2
  labs(x = "Agree/Neutral/Disagree", y = "Upvote Count", title = "Upvote Count vs Sentiment of Post Towards Topic of CMU") +
  scale_x_continuous(breaks = 1:3, labels = levels(unique_rows$Agree.Neutral.Disagree)) +  # Specify x-axis breaks and labels 
  scale_color_manual(values = c("red", "green", "blue")) +
  theme_minimal() 

ggplot(unique_rows, aes(x = as.numeric(Agree.Neutral.Disagree), y = Upvote.count, color = as.factor(subreddit))) +
  geom_jitter(aes(color = as.factor(subreddit)), width = 0.2, height = 0, alpha = 0.9) +
  geom_smooth(data = subset(unique_rows, subreddit == "CMU"), method = "lm", formula = y ~ poly(x, 2), se = FALSE, color = "aquamarine3") +
  geom_smooth(data = subset(unique_rows, subreddit == "ApplyingToCollege"), method = "lm", formula = y ~ poly(x, 2), se = FALSE, color = "coral3") +
  labs(x = "Agree/Neutral/Disagree", y = "Upvote Count", title = "Upvote Count vs Sentiment of Post Towards Topic of CMU by 
       Subreddit") +
  scale_x_continuous(breaks = 1:3, labels = levels(unique_rows$Agree.Neutral.Disagree)) +  # Specify x-axis breaks and labels 
  scale_color_manual(name = "Subreddit",
                     values = c("CMU" = "aquamarine3", "ApplyingToCollege" = "coral3")) +  # Changing legend names
  theme_minimal()

```

```{r}
# ggplot(unique_rows, aes(x = as.numeric(Agree.Neutral.Disagree), y = Upvote.Rate...., color = Agree.Neutral.Disagree)) +
#   geom_jitter(aes(color = as.factor(Agree.Neutral.Disagree)), width = 0.2, height = 0, alpha = 0.9) +
#   geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = FALSE, color = "black") +  # Add a polynomial regression line of degree 2
#   labs(x = "Agree/Neutral/Disagree", y = "Upvote Rate", title = "Upvote Rate vs Sentiment of Post Towards Topic of CMU") +
#   scale_x_continuous(breaks = 1:3, labels = levels(unique_rows$Agree.Neutral.Disagree)) +  # Specify x-axis breaks and labels 
#   # scale_color_manual(values = c("red", "green", "blue")) +
#   theme_minimal() 

ggplot(unique_rows, aes(x = as.numeric(Agree.Neutral.Disagree), y = Upvote.Rate...., color = as.factor(subreddit))) +
  geom_jitter(aes(color = as.factor(subreddit)), width = 0.2, height = 0, alpha = 0.9) +
  geom_smooth(data = subset(unique_rows, subreddit == "CMU"), method = "lm", formula = y ~ poly(x, 2), se = FALSE, color = "aquamarine3") +
  geom_smooth(data = subset(unique_rows, subreddit == "ApplyingToCollege"), method = "lm", formula = y ~ poly(x, 2), se = FALSE, color = "coral3") +
  labs(x = "Agree/Neutral/Disagree", y = "Upvote Rate", title = "Upvote Rate vs Sentiment of Post Towards Topic of CMU by 
       Subreddit") +
  scale_x_continuous(breaks = 1:3, labels = levels(unique_rows$Agree.Neutral.Disagree)) +  # Specify x-axis breaks and labels 
  scale_color_manual(name = "Subreddit",
                     values = c("CMU" = "aquamarine3", "ApplyingToCollege" = "coral3")) +  # Changing legend names
  theme_minimal()

# ggplot(unique_rows, aes(x = Reddit.ink.to.post, y = unique_rows$Upvote.Rate...., fill = Agree.Neutral.Disagree)) +
#   geom_bar(stat = "identity") +
#   facet_wrap(~ Agree.Neutral.Disagree, scales = "free_x") +
#   labs(x = "", y = "Total Views") +
#   theme_minimal() +
#   theme(axis.text.x = element_blank(),    # Remove x-axis text
#         axis.title.x = element_blank())   # Remove x-axis title

# reorder(Reddit.ink.to.post, Agree.Neutral.Disagree)

ggplot(unique_rows, aes(x = Reddit.ink.to.post, y = Upvote.Rate...., fill = Agree.Neutral.Disagree)) +
  geom_bar(stat = "identity") +
  facet_wrap(~ subreddit, scales = "free_x") +
  labs(x = "", y = "Upvote Rate") +
  theme_minimal() +
  theme(axis.text.x = element_blank(),    # Remove x-axis text
        axis.title.x = element_blank())   # Remove x-axis title

```

```{r}
# Define the custom order of levels
custom_order <- c("Agree", "Neutral", "Disagree")

# Reorder levels of Reddit.ink.to.post based on the custom order and Upvote Rate in decreasing order
unique_rows$Reddit.ink.to.post <- factor(unique_rows$Reddit.ink.to.post,
                                         levels = unique(unique_rows$Reddit.ink.to.post[order(unique_rows$Agree.Neutral.Disagree, -unique_rows$Upvote.Rate....)]))

# Plot with reordered levels
ggplot(unique_rows, aes(x = Reddit.ink.to.post, y = Upvote.Rate...., fill = Agree.Neutral.Disagree)) +
  geom_bar(stat = "identity") +
  facet_wrap(~ subreddit, scales = "free_x") +
  labs(x = "", y = "Upvote Rate", title = "Upvote Rate Across Subreddits by Sentiment of Post") +
  theme_minimal() +
  theme(axis.text.x = element_blank())    # Remove x-axis text
        # axis.title.x = element_blank())   # Remove x-axis title

# # Plot with reordered levels
# ggplot(unique_rows, aes(x = Post.Number, y = Upvote.Rate...., fill = Agree.Neutral.Disagree)) +
#   geom_bar(stat = "identity") +
#   facet_wrap(~ subreddit, scales = "free_x") +
#   labs(x = "", y = "Upvote Rate", title = "Upvote Rate Across Subreddits by Sentiment of Post") +
#   theme_minimal() +
#   theme(axis.text.x = element_blank())    # Remove x-axis text
#         # axis.title.x = element_blank())   # Remove x-axis title

```





```{r}

exclude_no_comment <- education[!is.na(education$Comment.word.count...use.chatgpt.), ]
# 
# ggplot(exclude_no_comment, aes(x = as.numeric(Agree.Neutral.Disagree), y = Comment.word.count...use.chatgpt., color = Agree.Neutral.Disagree)) +
#   geom_jitter(aes(color = as.factor(Agree.Neutral.Disagree)), width = 0.2, height = 0, alpha = 0.9) +
#   geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = FALSE, color = "black") +  # Add a polynomial regression line of degree 2
#   labs(x = "Agree/Neutral/Disagree", y = "Upvote Rate", title = "Upvote Rate vs Sentiment of Post Towards Topic of CMU") +
#   scale_x_continuous(breaks = 1:3, labels = levels(unique_rows$Agree.Neutral.Disagree)) +  # Specify x-axis breaks and labels 
#   # scale_color_manual(values = c("red", "green", "blue")) +
#   theme_minimal() 





ggplot(exclude_no_comment, aes(x = as.numeric(Agree.Neutral.Disagree), y = Comment.word.count...use.chatgpt., color = as.factor(subreddit))) +
  geom_jitter(aes(color = as.factor(subreddit)), width = 0.2, height = 0, alpha = 0.9) +
  geom_smooth(data = subset(unique_rows, subreddit == "CMU"), method = "lm", formula = y ~ poly(x, 2), se = FALSE, color = "aquamarine3") +
  geom_smooth(data = subset(unique_rows, subreddit == "ApplyingToCollege"), method = "lm", formula = y ~ poly(x, 2), se = FALSE, color = "coral3") +
  labs(x = "Agree/Neutral/Disagree", y = "Upvote Rate", title = "Upvote Rate vs Sentiment of Post Towards Topic of CMU by 
       Subreddit") +
  scale_x_continuous(breaks = 1:3, labels = levels(unique_rows$Agree.Neutral.Disagree)) +  # Specify x-axis breaks and labels 
  scale_color_manual(name = "Subreddit",
                     values = c("CMU" = "aquamarine3", "ApplyingToCollege" = "coral3")) +  # Changing legend names
  theme_minimal()


# Define the custom order of levels
custom_order <- c("Agree", "Neutral", "Disagree")

# Reorder levels of Reddit.ink.to.post based on the custom order and Upvote Rate in decreasing order
unique_rows$Reddit.ink.to.post <- factor(unique_rows$Reddit.ink.to.post,
                                         levels = unique(unique_rows$Reddit.ink.to.post[order(unique_rows$Agree.Neutral.Disagree, -unique_rows$Upvote.Rate....)]))

# Plot with reordered levels
ggplot(exclude_no_comment, aes(x = Reddit.ink.to.post, y = Comment.word.count...use.chatgpt., color = as.factor(subreddit))) +
  geom_bar(stat = "identity") +
  facet_wrap(~ subreddit, scales = "free_x") +
  labs(x = "", y = "Upvote Rate", title = ) +
  theme_minimal() +
  theme(axis.text.x = element_blank())    # Remove x-axis text

```

``` {r}
ggplot(exclude_no_comment, aes(x = Comment.word.count...use.chatgpt., color = as.factor(subreddit))) +
  geom_boxplot() +
  # facet_wrap(~ subreddit) +
  labs(x = "", y = "Comment Word Count", title = "Comment Word Count by Post", color = "Subreddit") +
  theme_minimal()

ggplot(exclude_no_comment, aes(x = Comment.word.count...use.chatgpt., color = as.factor(subreddit))) +
  geom_density() +
  # facet_wrap(~ subreddit) +
  labs(x = "", y = "Comment Word Count", title = "Comment Word Count by Post", color = "Subreddit") +
  theme_minimal()
  
# library(ggridges)
# 
# ggplot(exclude_no_comment, aes(x = Comment.word.count...use.chatgpt., y = as.factor(subreddit), fill = as.factor(subreddit))) +
#   geom_density_ridges(alpha = 0.5, scale = 0.7) +
#   labs(x = "Comment Word Count", y = "Subreddit", title = "Ridgeline Plot of Comment Word Count by Subreddit") +
#   theme_minimal()
```


```{r}
library(ggridges)

ggplot(exclude_no_comment, aes(x = Degree.of.Agreement.in.comment..1..Strongly.Disagree..10..Strongly.Agree.., color = as.factor(Agree.Neutral.Disagree))) +
  geom_density() +
  facet_wrap(~ subreddit) +
  labs(x = "Degree of Agreement in Comment (1: Strongly Disagree, 10: Strongly Agree)", y = "Density", title = "Level of Agreement from Comments Towards Original Post Sentiment", color = "Post Sentiment") +
  theme_minimal()
```

generally, across both subreddits, more comments are in disagreement rather than neutral or in agreement


in cmu, when the post is neutral, the comments have a lot of disagreement

in a2c, when it is disagree post, the comments have a lot more disagree
but in general, there is a lot 



```{r}
ggplot(exclude_no_comment, aes(x = Degree.of.Agreement.in.comment..1..Strongly.Disagree..10..Strongly.Agree.., 
       y = Degree.of.Hostility..1..Very.Friendly..10..Very.Hostile., color = factor(subreddit))) +
  geom_point() +
  geom_smooth(se = FALSE, method = "lm", formula = y~x) +
  labs(x = "Degree of Agreement (1. Strongly Disagree, 10. Strongly Agree)", 
       y = "Degree of Hostility (1. Very Friendly, 10. Very Hostile)", 
       title = "Degree of Hostility in Comment vs Degree of Agreement in Comment") +
  scale_color_discrete()

ggplot(exclude_no_comment, aes(x = Degree.of.Hostility..1..Very.Friendly..10..Very.Hostile., 
       y = exclude_no_comment$Comment.word.count...use.chatgpt., color = factor(subreddit))) +
  geom_point() +
  geom_smooth(se = FALSE, method = "lm", formula = y~x) +
  labs(x = "Degree of Hostility (1. Very Friendly, 10. Very Hostile)", 
       y = "Comment Word Count", 
       title = "Word Count of Comments vs Hostility of Comments")

ggplot(exclude_no_comment, aes(x = Degree.of.Agreement.in.comment..1..Strongly.Disagree..10..Strongly.Agree.., 
       y = exclude_no_comment$Comment.word.count...use.chatgpt., color = factor(subreddit))) +
  geom_point() +
  geom_smooth(se = FALSE, method = "lm", formula = y~x) +
  labs(x = "Degree of Agreement (1. Strongly Disagree, 10. Strongly Agree)", 
       y = "Comment Word Count", 
       title = "Word Count of Comments vs Agreement of Comments")
```


increased agreement => less hostile
more general subreddit decreases in hostility faster as agreement increases

increased hostile => less words 
increased agreement => more words
cmu has a higher base level of word count for the comments





```{r}

# Create a data frame with the number of comments per post number
# comments_df <- data.frame(Post_Number = unique(education$Post.Number),
#                           Number_of_Comments = as.vector(table(education$Raw.comment)))

comments_df <- education %>%
  group_by(Post.Number) %>%
  summarise(Raw.comment = n())

comments_df

# Replace specific post numbers with 0
comments_df$Number_of_Comments[comments_df$Post_Number %in% c("1.2", "2.2")] <- 0

comments_df <- transform(comments_df, Category = ifelse(grepl("^1\\.", Post_Number), "A2C", "CMU"))


# Plot using ggplot2
ggplot(comments_df, aes(x = Post_Number, y = Number_of_Comments, fill = )) +
  geom_bar(stat = "identity") +
  labs(x = "Post Number", y = "Number of Comments", title = "Number of Comments per Post")



```





