---
title: "bubbles final graphs"
output: html_document
date: "2024-03-17"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
education <- read.csv("/Users/andyouyang/Documents/bubbles final.csv")

education$Agree.Neutral.Disagree <- factor(education$Agree.Neutral.Disagree, levels = c("agree", "neutral", "disagree"))
unique_rows <- education[!duplicated(education$Reddit.ink.to.post), ]
```




```{r}
ggplot(unique_rows, aes(x = Post.Number, y = Total.Views, fill = Agree.Neutral.Disagree)) +
  geom_bar(stat = "identity") +
  facet_wrap(~ Agree.Neutral.Disagree, scales = "free_x") +
  labs(x = "Post Number", y = "Total Views", title = "Total Views Across Subreddits by Sentiment of Post") +
  facet_wrap(~ subreddit, scales = "free_x")

custom_order <- c("Agree", "Neutral", "Disagree")

unique_rows$Post.Number <- factor(unique_rows$Post.Number,
                                         levels = unique(unique_rows$Post.Number[order(unique_rows$Agree.Neutral.Disagree, -unique_rows$Upvote.Rate....)]))

ggplot(unique_rows, aes(x = Post.Number, y = Upvote.Rate...., fill = Agree.Neutral.Disagree)) +
  geom_bar(stat = "identity") +
  facet_wrap(~ subreddit, scales = "free_x") +
  labs(x = "Post Number", y = "Upvote Rate", title = "Upvote Rate Across Subreddits by Sentiment of Post")
```



```{r}
ggplot(exclude_no_comment, aes(x = Comment.word.count...use.chatgpt., color = as.factor(subreddit))) +
  geom_density() +
  # facet_wrap(~ subreddit) +
  labs(x = "Comment Word Count", y = "Density", title = "Density Distributions of Comment Word Count by Subreddit", color = "Subreddit") +
  theme_minimal()

ggplot(exclude_no_comment, aes(x = Comment.word.count...use.chatgpt., color = as.factor(subreddit))) +
  geom_boxplot() +
  # facet_wrap(~ subreddit) +
  labs(x = "", y = "Comment Word Count", title = "Comment Word Count by Subreddit", color = "Subreddit") +
  theme_minimal()
```

```{r}
ggplot(exclude_no_comment, aes(x = Degree.of.Agreement.in.comment..1..Strongly.Disagree..10..Strongly.Agree.., color = as.factor(Agree.Neutral.Disagree))) +
  geom_density() +
  facet_wrap(~ subreddit) +
  labs(x = "Degree of Agreement in Comment (1: Strongly Disagree, 10: Strongly Agree)", y = "Density", title = "Level of Agreement from Comments Towards Original Post Sentiment", color = "Post Sentiment") +
  theme_minimal()
```
generally, across both subreddits, more comments are in disagreement rather than neutral or in agreement


in cmu, when the post is neutral, the comments have a lot of disagreement

in a2c, when it is disagree post, the comments have a lot more disagree
but in general, there is a lot 


```{r}
ggplot(exclude_no_comment, aes(x = Degree.of.Agreement.in.comment..1..Strongly.Disagree..10..Strongly.Agree.., 
       y = Degree.of.Hostility..1..Very.Friendly..10..Very.Hostile., color = factor(subreddit))) +
  geom_point() +
  geom_smooth(se = FALSE, method = "loess", formula = y~x) +
  labs(x = "Degree of Agreement (1. Strongly Disagree, 10. Strongly Agree)", 
       y = "Degree of Hostility (1. Very Friendly, 10. Very Hostile)", 
       title = "Degree of Hostility in Comment vs Degree of Agreement in Comment") +
  scale_color_discrete()

ggplot(exclude_no_comment, aes(x = Degree.of.Hostility..1..Very.Friendly..10..Very.Hostile., 
       y = exclude_no_comment$Comment.word.count...use.chatgpt., color = factor(subreddit))) +
  geom_point() +
  geom_smooth(se = FALSE, method = "loess", formula = y~x) +
  labs(x = "Degree of Hostility (1. Very Friendly, 10. Very Hostile)", 
       y = "Comment Word Count", 
       title = "Word Count of Comments vs Hostility of Comments")

ggplot(exclude_no_comment, aes(x = Degree.of.Agreement.in.comment..1..Strongly.Disagree..10..Strongly.Agree.., 
       y = exclude_no_comment$Comment.word.count...use.chatgpt., color = factor(subreddit))) +
  geom_point() +
  geom_smooth(se = FALSE, method = "loess", formula = y~x) +
  labs(x = "Degree of Agreement (1. Strongly Disagree, 10. Strongly Agree)", 
       y = "Comment Word Count", 
       title = "Word Count of Comments vs Agreement of Comments")
```

increased agreement => less hostile
more general subreddit decreases in hostility faster as agreement increases

increased hostile => less words 
increased agreement => more words
cmu has a higher base level of word count for the comments

# upvote count vs agree & upvote count vs hostile
```{r}
ggplot(exclude_no_comment, aes(x = Degree.of.Agreement.in.comment..1..Strongly.Disagree..10..Strongly.Agree.., 
       y = exclude_no_comment$Comment.upvote.count, color = factor(subreddit))) +
  geom_point() +
  geom_smooth(se = FALSE, method = "loess", formula = y~x) +
  labs(x = "Degree of Agreement (1. Strongly Disagree, 10. Strongly Agree)", 
       y = "Comment Upvote Count", 
       title = "Word Count of Comments vs Agreement of Comments")

ggplot(exclude_no_comment, aes(x = Degree.of.Hostility..1..Very.Friendly..10..Very.Hostile., 
       y = exclude_no_comment$Comment.upvote.count, color = factor(subreddit))) +
  geom_point() +
  geom_smooth(se = FALSE, method = "loess", formula = y~x) +
  labs(x = "Degree of Agreement (1. Strongly Disagree, 10. Strongly Agree)", 
       y = "Comment Upvote Count", 
       title = "Word Count of Comments vs Agreement of Comments")
```
```

